Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-09 FDT2020/Introduction.tex
Adding a section label
unified Subtour elimination and multi-graph notation

In general the integrality gap is defined similarly for any objective function, but we wish to be explicit about the class of problems we assume in this paper. For example consider the minimum cost \textsc{2-edge-connected multi-subgraph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multiedges allowed. A graph is 2-edge-connected if there are at least two edge-disjoint paths between every pair of vertices.  A linear programming relaxation for this problem, known as the {\em subtour-elimination} relaxation, is
 \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in [0,2]^{E}\}, 
 \label{eq:subtour}
 \end{equation}
where $\delta(U)$ for vertex subset $U$ is the set of edges that cross the cut defined by $U$.  That is, each $e \in \delta(U)$ has one endpoint in $U$ and the other endpoint in $V-U$.
 In this case the instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2EC on a graph with $n$ vertices. Alexander et al. \cite{alexander2006integrality} showed this instance-specific integrality gap
%of the subtour elimination relaxation for the 2EC
is at most $\frac{7}{6}$ for instances with $n= 10$ .

The value of $g(I)$ depends on the constraints in~(\ref{S}).  We cannot hope to find solutions for the IP with objective values better than $g(I)\cdot z_{LP}(I,c)$. More generally we can define the integrality gap for a class of instances $\mathcal{I}$ as follows.% In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}\label{gapproblem}
g(\mathcal{I}) = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}.
\end{equation}
For example, the integrality gap of the subtour elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}. Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation to bound the quality of a feasible solution.

@@

One can extend the FDT algorithm for binary IPs into covering\footnote{A covering IP has nonnegative constraint matrix, objective coefficients and right-hand side ($A,b,c$).} $\{0,1,2\}$ IPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT. To eradicate this extra factor, we must treat the coordinate $i$ with $x_i=1$ differently. In Section~\ref{sec:2EC} we focus on the 2-edge-connected multi-subgraph graph problem (2EC) defined above.  It's subtour-elimination LP relaxation is given in (\ref{eq:subtour}).
%}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph of $G$ with minimum cost. The natural linear programming relaxation for this problem is 
%\begin{equation}
%\min \{cx \; : \; x(\delta(U))\geq 2 \; \text{ for }\emptyset \subset U \subset V, \; x\in [0,2]^E\}
%\end{equation}
For input graph $G$, let $\subtour(G)$ denote the feasible region of this LP. Let $\2ec(G)$ be the convex hull of incidence vectors\footnote{The incidence vector $x$ of a 2-edge-connected multigraph has an element for each edge $e$, with $x_e \in \{0,1,2\}$ indicating the number of times edge $e$ appears in the solution.} of 2-edge-connected multi-subgraphs of graph $G$. Following the definition in (\ref{gapproblem}) have
\begin{equation}
g(\2ec) = \max_{c\geq 0 , G}\frac{\min_{x\in \2ec(G)} cx}{\min_{x\in \subtour(G)} cx}.
\end{equation}

@@

\subsubsection{2-edge-connected multi-subgraph problem}
Known polyhedral structure makes it easier to study integrality gaps for such problems. We use the idea of fundamental extreme point \cite{carrravi,boydcarr,Carr2004} to create the ``hardest'' LP solutions to decompose.

There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP, see \cite{tspbook}) or 2EC.
%\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices. Alexander et al. \cite{alexander2006integrality} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $g(\2ec)$ on graphs with at most 10 vertices.

>>>>

In general the integrality gap is defined similarly for any objective function, but we wish to be explicit about the class of problems we assume in this paper. For example consider the minimum cost \textsc{2-edge-connected multi-subgraph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multi-edges allowed. A graph is 2-edge-connected if there are at least two edge-disjoint paths between every pair of vertices.  A linear programming relaxation for this problem, known as the {\em subtour-elimination} relaxation, is
 \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in [0,2]^{E}\}, 
 \label{eq:subtour}
 \end{equation}
where $\delta(U)$ for vertex subset $U$ is the set of edges that cross the cut defined by $U$.  That is, each $e \in \delta(U)$ has one endpoint in $U$ and the other endpoint in $V-U$.
 In this case the instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2EC on a graph with $n$ vertices. Alexander et al. \cite{alexander2006integrality} showed this instance-specific integrality gap
%of the subtour elimination relaxation for the 2EC
is at most $\frac{7}{6}$ for instances with $n= 10$ .

The value of $g(I)$ depends on the constraints in~(\ref{S}).  We cannot hope to find solutions for the IP with objective values better than $g(I)\cdot z_{LP}(I,c)$. More generally we can define the integrality gap for a class of instances $\mathcal{I}$ as follows.% In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}\label{gapproblem}
g(\mathcal{I}) = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}.
\end{equation}
For example, the integrality gap of the subtour-elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}. Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation to bound the quality of a feasible solution.

@@

One can extend the FDT algorithm for binary IPs into covering\footnote{A covering IP has nonnegative constraint matrix, objective coefficients and right-hand side ($A,b,c$).} $\{0,1,2\}$ IPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT. To eradicate this extra factor, we must treat the coordinate $i$ with $x_i=1$ differently. In Section~\ref{sec:2EC} we focus on the 2-edge-connected multi-subgraph graph problem (2EC) defined above.  It's subtour-elimination LP relaxation is given in (\ref{eq:subtour}).
%}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph of $G$ with minimum cost. The natural linear programming relaxation for this problem is 
%\begin{equation}
%\min \{cx \; : \; x(\delta(U))\geq 2 \; \text{ for }\emptyset \subset U \subset V, \; x\in [0,2]^E\}
%\end{equation}
For input graph $G$, let $\subtour(G)$ denote the feasible region of this LP. Let $\2ec(G)$ be the convex hull of incidence vectors\footnote{The incidence vector $x$ of a 2-edge-connected multi-subgraph has an element for each edge $e$, with $x_e \in \{0,1,2\}$ indicating the number of times edge $e$ appears in the solution.} of 2-edge-connected multi-subgraphs of graph $G$. Following the definition in (\ref{gapproblem}) have
\begin{equation}
g(\2ec) = \max_{c\geq 0 , G}\frac{\min_{x\in \2ec(G)} cx}{\min_{x\in \subtour(G)} cx}.
\end{equation}

@@

\subsubsection{2-edge-connected multi-subgraph problem}
\label{sec:2EC-intro}
Known polyhedral structure makes it easier to study integrality gaps for such problems. We use the idea of fundamental extreme point \cite{carrravi,boydcarr,Carr2004} to create the ``hardest'' LP solutions to decompose.

There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP, see \cite{tspbook}) or 2EC.
%\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour-elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices. Alexander et al. \cite{alexander2006integrality} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $g(\2ec)$ on graphs with at most 10 vertices.

### 2020-08-09 FDT2020/conclusion.tex
unified Subtour elimination and multi-graph notation

The results in Sections \ref{sec:domTOIP}, \ref{sec:binaryfdt}  and \ref{sec:2EC} hold if the intial integer program has some auxilliary continuous variables\footnote{Here by auxilliary variables we mean a variable that does not participate in the objective function}. That is, when we have 
\begin{equation*}
S(A,b) = \{x\in \mathbb{Z}^n\times \mathbb{R}^p: Ax\geq b\},
\end{equation*}
where the last $p$ variables are continous, $P(A,b) = \{x\in \mathbb{R}^n: Ax\geq b\}$
\cindy{should this be $P(A,b) = \{x\in \mathbb{R}^{n+p}: Ax\geq b\}$?}
and define
\begin{equation*}
g(I) = \max_{c\in \mathbb{R}^n_+}\frac{\min_{x\in S(A,b)} \sum_{i=1}^{n}c_ix_i}{\min_{x\in P(A,b)} \sum_{i=1}^{n}c_ix_i},
\end{equation*}
our main results work. In fact our implementation of the subtour elimination formulation is based on an extended formulation with auxiliary variables (see \cite{subtour-extended}). We removed this extension to make the presentation simpler.

>>>>

The results in Sections \ref{sec:domTOIP}, \ref{sec:binaryfdt}  and \ref{sec:2EC} hold if the intial integer program has some auxilliary continuous variables\footnote{Here by auxilliary variables we mean a variable that does not participate in the objective function}. That is, when we have 
\begin{equation*}
S(A,b) = \{x\in \mathbb{Z}^n\times \mathbb{R}^p: Ax\geq b\},
\end{equation*}
where the last $p$ variables are continous, $P(A,b) = \{x\in \mathbb{R}^{n+p}: Ax\geq b\}$
%\cindy{should this be $P(A,b) = \{x\in \mathbb{R}^{n+p}: Ax\geq b\}$?}
and define
\begin{equation*}
g(I) = \max_{c\in \mathbb{R}^n_+}\frac{\min_{x\in S(A,b)} \sum_{i=1}^{n}c_ix_i}{\min_{x\in P(A,b)} \sum_{i=1}^{n}c_ix_i},
\end{equation*}
our main results work. In fact our implementation of the subtour-elimination relaxation is based on an extended formulation with auxiliary variables (see \cite{subtour-extended}). We removed this extension to make the presentation simpler.

### 2020-08-09 FDT2020/main-section.tex
unified Subtour elimination and multi-graph notation

As described in Section~\ref{sec:2EC-intro}, when the LP optimum for (\ref{eq:subtour}) is a Carr-Vempala point (see Figure~\ref{fig:CVpoint}), the integrality gap of that instance is equal to that of 2EC. So in that sense, these are the hardest fractional points to round to a feasible solution. We now compare the quality of FDT's solution from a Carr-Vempala point to that of Christofides, the best known approximation algorithm.  In the classic graph-based Christofides algorithm for TSP, find a minimum spanning tree of the graph.  Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)graph 2-edge-connected. If we stop that algorithm without shortcutting, we have a feasible solution for Metric-2EC (given a complete graph, find the minimum-cost 2-edge-connected subgraph, with no multiedges).
\arash{The following sentence is not accurate, Metric-TSP is the same as TSP on a non-complete graph where we can take multiple copies of the edges, Metric-2EC (given complete graph with metric costs find the minimum cost 2-edge-connected SUBgraph -no doubling of edges-) is the same as 2EC on a non-complete graph where we can take multiple copies of edges.}
\cindy{It sounded like 2EC doesn't assume a complete graph.  But I removed the sentence.  Is the following OK?}
For 2EC, instead of a matching, we add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$. Graphs always have an even number of odd vertices since every edge has two endpoints, giving an even number of endpoints.}. The best-of-many Christofides (BOMC) algorithm~\cite{AKS15} works better than the classic Christofides algorithm in practice~\cite{GW17}.  The BOMC algorithm samples many spanning trees from the LP relaxation (with edges chosen proportionally to the LP value), augments each spanning tree with the matching, and takes the best solution.

\arash{I think here we should say that something like this: the polyhedral analaysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multigraph of $G$ \cite{wolsey,shmoyswilliamson}. This bound holds for any point $x\in \subtour(G)$ for any graph $G$, including any Carr-Vempala point. Below we ask if this bound can be improved for specific instances by doing a slightly improved analysis of the algorithm}\arash{Then we explain the LP in (32)} 
\cindy{I like that and have added it, but I don't think it is too much detail to walk the reader through the decompositions.}

The polyhedral analysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multigraphs of $G$~\cite{wolsey,shmoyswilliamson}. This bound holds for any point $x\in \subtour(G)$ for any graph $G$, including any Carr-Vempala point. We show how this bound can be improved for specific instances by doing a slightly improved analysis of the algorithm.

@@

Let $x$ be a Carr-Vempala point (from~(\ref{eq:subtour})) defined on a graph $G=(V,E)$. \arash{I think it's better to say that: It is a well-known fact that if $x\in \subtour(G)$, then $\frac{|V|-1}{|V|}x$ can be written as a convex combination of spanning trees of $G$ (See Proposition 2 in \cite{Vygen12} for instance), the reason is that this is because Vygen didn't come up with this.}

@@

Let $O_i$ be the set of odd-degree vertices of spanning tree $T_i$.
%Consider the incidence vectors of feasible $O_i$-joins.
% \cindy{Arash, do you also want to replace this longer discussion with a reference?}
Adding an $O_i$-join to tree $T_i$ gives a solution to 2EC.
% CAP: TODO, use later?
%Let $S$ be any subset of vertices with an even number of odd-degree vertices.  The $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices. The subtour-elimination LP requires every subset of vertices have two edges connecting it to the rest of the vertices.  Therefore, since $x$ is a feasible solution to the subtour-elimination LP, $x/2$ is feasible for the $O_i$-join LP associated with spanning tree $T_i$.
\arash{I still think this following sentence is confusing: we are not using the observation of Wolsey. Actually I don't think Wolsey spefically talks about writing 3/2x as a convex combination of solutions... I think it's would be better if we just explain how $(\frac{|V|-1}{|V|} + \alpha) x$ as convex combination of solutions and cite Wolsey as a general thing. How about deleting the next sentence, and after describing the LP below saying that $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ is a feasible solution to this LP yielding an integrality gap of $\frac{3}{2}$ for the subtour-elimination relaxation for the TSP \cite{wolsey}.}
%We will use Wolsey's observation~\cite{wolsey} that $\frac{x}{2}$ is in the convex hull of incidence vectors of the $O_i$-join of $G$ (denoted $O_i\join(G)$).
%\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}
%\cindy{Do you have to precompute the joins (If they are more than the spanning trees themselves)?  Does that mean generating spanning trees before setting up the LP?  Or generating them on the fly?  Only minimum-weight spanning trees?  It seems that with a little more explanation, a reader who has not been immersed in 2EC and TSP could follow this.}
We solve the following LP that allows us to find edges that simultaneously augment all the spanning trees to solutions to 2EC.
%$O$-join-based parity corrections that are good for the whole convex combination.
\begin{equation}\label{ojoinaverage}
\min \{ \alpha:\;\sum_{i=1}^{k} \lambda_i y^i = \alpha \cdot x,\;  y^i \in \dom(O_i\join(G)) \; \mbox{for $i\in [k]$}\}.
\end{equation}
The variables in the above LP are $y^i\in \mathbb{R}^{E}_{\geq 0}$ for $i\in [k]$, where $E$ is the number of edges in the graph.  The parameters $\lambda_i$ are those we computed in~(\ref{eq:tree-decomp}). For each $i\in [k]$, we require $y^i$ to be in the dominant of $O_i\join(G)$.  We enforce this by adding a set of constraints for each $i$ from~\cite[p. 490]{schrijverbook}. These constraints force the inclusion of at least one edge from the cut associated with each set of vertices that have an even number of elements from $O_i$. The  $y^i$ need not be integer vectors. Because the $O_i$-join polytope is integral, we can replace $y^i$ with a convex combination of $O_i$-joins of $G$ (proposition~\ref{cara}). Setting $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ gives a feasible solution to this LP, yielding the integarlity gap of $\frac{3}{2}$ of the subtour elimination relaxation for the TSP \cite{wolsey}. More generally, this method gives a ($\frac{|V|-1}{|V|}+\alpha$)-approximation for the specific instance $x$. % In general this can be less than the classic $\frac{3}{2}$.

>>>>

As described in Section~\ref{sec:2EC-intro}, when the LP optimum for (\ref{eq:subtour}) is a Carr-Vempala point (see Figure~\ref{fig:CVpoint}), the integrality gap of that instance is equal to that of 2EC. So in that sense, these are the hardest fractional points to round to a feasible solution. We now compare the quality of FDT's solution from a Carr-Vempala point to that of Christofides, the best known approximation algorithm.  In the classic graph-based Christofides algorithm for TSP, find a minimum spanning tree of the graph.  Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)-subgraph 2-edge-connected. If we stop that algorithm without shortcutting, we have a feasible solution for Metric-2EC (given a complete graph, find the minimum-cost 2-edge-connected subgraph, with no multiedges).
\arash{The following sentence is not accurate, Metric-TSP is the same as TSP on a non-complete graph where we can take multiple copies of the edges, Metric-2EC (given complete graph with metric costs find the minimum cost 2-edge-connected SUBgraph -no doubling of edges-) is the same as 2EC on a non-complete graph where we can take multiple copies of edges.}
\cindy{It sounded like 2EC doesn't assume a complete graph.  But I removed the sentence.  Is the following OK?}
\arash{Still not quite accurate. The sentence gives the impression that changing matching with $T$-join is the difference between TSP and 2EC, but its the difference between working with complete graph with metric costs and a non-complete graph where doubling edges is allowed.}
For 2EC, instead of a matching, we add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$. Graphs always have an even number of odd vertices since every edge has two endpoints, giving an even number of endpoints.}. The best-of-many Christofides (BOMC) algorithm~\cite{AKS15} works better than the classic Christofides algorithm in practice~\cite{GW17}.  The BOMC algorithm samples many spanning trees from the LP relaxation (with edges chosen proportionally to the LP value), augments each spanning tree with the matching, and takes the best solution.

%\arash{I think here we should say that something like this: the polyhedral analaysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multigraph of $G$ \cite{wolsey,shmoyswilliamson}. This bound holds for any point $x\in \subtour(G)$ for any graph $G$, including any Carr-Vempala point. Below we ask if this bound can be improved for specific instances by doing a slightly improved analysis of the algorithm}\arash{Then we explain the LP in (32)} 
%\cindy{I like that and have added it, but I don't think it is too much detail to walk the reader through the decompositions.}

The polyhedral analysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multi-subgraphs of $G$~\cite{wolsey,shmoyswilliamson}. This bound holds for any point $x\in \subtour(G)$ for any graph $G$, including any Carr-Vempala point. We show how this bound can be improved for specific instances by doing a slightly improved analysis of the algorithm.

@@

Let $x$ be a Carr-Vempala point (from~(\ref{eq:subtour})) defined on a graph $G=(V,E)$. %\arash{I think it's better to say that: It is a well-known fact that if $x\in \subtour(G)$, then $\frac{|V|-1}{|V|}x$ can be written as a convex combination of spanning trees of $G$ (See Proposition 2 in \cite{Vygen12} for instance), the reason is that this is because Vygen didn't come up with this.}

@@

Let $O_i$ be the set of odd-degree vertices of spanning tree $T_i$.
%Consider the incidence vectors of feasible $O_i$-joins.
% \cindy{Arash, do you also want to replace this longer discussion with a reference?}
Adding an $O_i$-join to tree $T_i$ gives a solution to 2EC.
% CAP: TODO, use later?
%Let $S$ be any subset of vertices with an even number of odd-degree vertices.  The $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices. The subtour-elimination LP requires every subset of vertices have two edges connecting it to the rest of the vertices.  Therefore, since $x$ is a feasible solution to the subtour-elimination LP, $x/2$ is feasible for the $O_i$-join LP associated with spanning tree $T_i$.
%\arash{I still think this following sentence is confusing: we are not using the observation of Wolsey. Actually I don't think Wolsey spefically talks about writing 3/2x as a convex combination of solutions... I think it's would be better if we just explain how $(\frac{|V|-1}{|V|} + \alpha) x$ as convex combination of solutions and cite Wolsey as a general thing. How about deleting the next sentence, and after describing the LP below saying that $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ is a feasible solution to this LP yielding an integrality gap of $\frac{3}{2}$ for the subtour-elimination relaxation for the TSP \cite{wolsey}.}
%We will use Wolsey's observation~\cite{wolsey} that $\frac{x}{2}$ is in the convex hull of incidence vectors of the $O_i$-join of $G$ (denoted $O_i\join(G)$).
%\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}
%\cindy{Do you have to precompute the joins (If they are more than the spanning trees themselves)?  Does that mean generating spanning trees before setting up the LP?  Or generating them on the fly?  Only minimum-weight spanning trees?  It seems that with a little more explanation, a reader who has not been immersed in 2EC and TSP could follow this.}
We solve the following LP that allows us to find edges that simultaneously augment all the spanning trees to solutions to 2EC.
%$O$-join-based parity corrections that are good for the whole convex combination.
\begin{equation}\label{ojoinaverage}
\min \{ \alpha:\;\sum_{i=1}^{k} \lambda_i y^i = \alpha \cdot x,\;  y^i \in \dom(O_i\join(G)) \; \mbox{for $i\in [k]$}\}.
\end{equation}
The variables in the above LP are $y^i\in \mathbb{R}^{E}_{\geq 0}$ for $i\in [k]$, where $E$ is the number of edges in the graph.  The parameters $\lambda_i$ are those we computed in~(\ref{eq:tree-decomp}). For each $i\in [k]$, we require $y^i$ to be in the dominant of $O_i\join(G)$.  We enforce this by adding a set of constraints for each $i$ from~\cite[p. 490]{schrijverbook}. These constraints force the inclusion of at least one edge from the cut associated with each set of vertices that have an even number of elements from $O_i$. The  $y^i$ need not be integer vectors. Because the $O_i$-join polytope is integral, we can replace $y^i$ with a convex combination of $O_i$-joins of $G$ (proposition~\ref{cara}). Setting $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ gives a feasible solution to this LP, yielding the integarlity gap of $\frac{3}{2}$ of the subtour-elimination relaxation for the TSP \cite{wolsey}. More generally, this method gives a ($\frac{|V|-1}{|V|}+\alpha$)-approximation for the specific instance $x$. % In general this can be less than the classic $\frac{3}{2}$.
